Exploratory Data Analysis

### 2019-09-12 hw1/results/Exploratory Data Analysis.Rmd
More work on HW 1 EDA

---
title: "Exploratory Data Analysis"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---

>>>>

---
title: "Exploratory Data Analysis"
author: "Critical Thinking Group 3"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---
